\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{tfrupee}
\geometry{a4paper, margin=1in}

\begin{document}

\section*\textbf{Question numbers 1 to 10 carry 3 marks each.}
\begin{enumerate}

\item \textbf{}Solve the system of equations:

$\frac{bx}{a} - \frac{a y}{b} + a + b = 0 \quad \text{and} \quad b x - a y + 2ab = 0.$

\item Given that:\\

$P$ = $\frac{x+2y}{x+y} + \frac{x}{y}, $Q$=\frac{x+y}{x-y}-\frac{x-y}{x+y}$\quad and $R$=$\frac{x+2y}{x+y}$ - $\frac{x}{x+y}$  \\

\item If $(x + 2)(x - 3)$ is the HCF of the polynomials $p(x) = (x^2 + x - 2)(3x^2 - 8x + c)$ and $q(x) = (x^2 + x - 12)(2x^2 + x + b),$ \\
find the values of $c$ and $b$.

\item  Using the quadratic formula, solve the equation: $A^2 b^2 x^2 - (4b^4 - 3a^4) x - 12 a^2 b^2 = 0.$

\item  A household article is available for \rupee970 cash or \rupee 210 cash down payment followed by three equal monthly installments. If the rate of interest charged under the installment plan is 16\% per annum, find the amount of each installment \\

\item A man borrows \rupee 25,200 from a finance company and has to repay it in two equal annual installments. If the interest is charged at the rate of 10\% per annum compounded annually, calculate the amount of each installment.

\item The speed of a boat in still water is 11 km/hr. It can go 12 km upstream and return 
downstream to the original point in 2 hours 45 minutes. Find the speed of the stream.

\item A bucket made up of a metal sheet is in the form of a frustum of a cone. Its depth is $24\text{ cm}$ and the diameters of the top and bottom are $30\text{ cm}$ and $10\text{ cm}$ respectively. Find the cost of milk which can completely fill the bucket at the rate of \rupee 20 per liter and the cost of the metal sheet used, if it costs \rupee10 per $100\text{ cm}^2$. $(Use \pi=3.14)$


\item Mrs. Ruchi's salary is $\text{Rs.} 32,250$ per month exclusive of HRA. She donates \rupee 12,000 to Prime Minister's Relief Fund ($100\%$ exemption). She also donates \rupee 6,000 to a school and gets a relief of $50\%$ on this donation. She contributes \rupee5,000 per month towards her Provident Fund. She pays a quarterly premium of $\text{Rs.} 2,500$ towards her LIC policy and invests \rupee 25,000 in NSCs. If \rupee 2,700 is the tax deducted each month from her salary for $11$ months, find the tax deducted from her salary in the last month of the year.

\textbf{Income Tax Rates:}

\begin{tabular}{|l|l|}
\hline
Slab & Tax Rate \\
\hline
Up to $\text{Rs.} 1,35,000$ & No tax \\
\hline
From $\text{Rs.} 1,35,001$ to $\text{Rs.} 1,50,000$ & $10\%$ of the taxable income above $\text{Rs.} 1,35,000$ \\
\hline
From $\text{Rs.} 1,50,001$ to $\text{Rs.} 2,50,000$ & $\text{Rs.} 1,500 + 20\%$ of the income exceeding $\text{Rs.} 1,50,000$ \\
\hline
$\text{Rs.} 2,50,001$ and above & $\text{Rs.} 21,500 + 30\%$ of the amount exceeding $\text{Rs.} 2,50,000$ \\
\hline
\end{tabular}

\textbf{Education Cess:} $2\%$ of the income tax


\end{enumerate}
\end{document}
